% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}

\hypertarget{the-letter-of-st.-paul-to-philemon}{%
\section{The Letter of St.~Paul to
Philemon}\label{the-letter-of-st.-paul-to-philemon}}

\hypertarget{chapter-1}{%
\subsection{Chapter 1}\label{chapter-1}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Paul, a prisoner of Christ Jesus, and Timothy, a brother: to Philemon,
  our beloved and fellow labourer, \^{}1-1
\item
  And to Appia, our dearest sister, and to Archippus, our fellow
  soldier, and to the church which is in thy house. \^{}1-2
\item
  Grace to you and peace, from God our Father and from the Lord Jesus
  Christ. \^{}1-3
\item
  I give thanks to my God, always making a remembrance of thee in my
  prayers. \^{}1-4
\item
  Hearing of thy charity and faith, which thou hast in the Lord Jesus
  and towards all the saints: \^{}1-5
\item
  That the communication of thy faith may be made evident in the
  acknowledgment of every good work that is in you in Christ Jesus.
  \^{}1-6
\item
  For I have had great joy and consolation in thy charity, because the
  bowels of the saints have been refreshed by thee, brother. \^{}1-7
\item
  Wherefore, though I have much confidence in Christ Jesus to command
  thee that which is to the purpose: \^{}1-8
\item
  For charity sake I rather beseech, whereas thou art such a one, as
  Paul, an old man and now a prisoner also of Jesus Christ. \^{}1-9
\item
  I beseech thee for my son, whom I have begotten in my bands, Onesimus,
  \^{}1-10
\item
  Who hath been heretofore unprofitable to thee but now is profitable
  both to me and thee: \^{}1-11
\item
  Whom I have sent back to thee. And do thou receive him as my own
  bowels. \^{}1-12
\item
  Whom I would have retained with me, that in thy stead he might have
  ministered to me in the bands of the gospel. \^{}1-13
\item
  But without thy counsel I would do nothing: that thy good deed might
  not be as it were of necessity, but voluntary. \^{}1-14
\item
  For perhaps he therefore departed for a season from thee that thou
  mightest receive him again for ever: \^{}1-15
\item
  Not now as a servant, but instead of a servant, a most dear brother,
  especially to me. But how much more to thee, both in the flesh and in
  the Lord? \^{}1-16
\item
  If therefore thou count me a partner, receive him as myself. \^{}1-17
\item
  And if he hath wronged thee in any thing or is in thy debt, put that
  to my account. \^{}1-18
\item
  I Paul have written it with my own hand: I will repay it: not to say
  to thee that thou owest me thy own self also. \^{}1-19
\item
  Yea, brother. May I enjoy thee in the Lord! Refresh my bowels in the
  Lord. \^{}1-20
\item
  Trusting in thy obedience, I have written to thee: knowing that thou
  wilt also do more than I say. \^{}1-21
\item
  But withal prepare me also a lodging. For I hope that through your
  prayers I shall be given unto you. \^{}1-22
\item
  There salute thee Epaphras, my fellow prisoner in Christ Jesus:
  \^{}1-23
\item
  Mark, Aristarchus, Demas and Luke, my fellow labourers. \^{}1-24
\item
  The grace of our Lord Jesus Christ be with your spirit. Amen. \^{}1-25
\end{enumerate}

\end{document}
